\pdftitle

### 2017-05-15 maxNt.tex
more discussion

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2017-05-15T17:53:53+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

The probability distribution for the sample average obtained by applying
\me\ at the population level has by construction a lower entropy than the
one obtained by application at the sample level. It says that some sample
states $\yx$ should be considered less likely than in the other
distribution. The lower entropy signals the presence of an additional
physical assumption behind the former distribution. Such assumption,
intuitively, is that the sample is part of a larger population, of which it
is representative. And this assumption may affect our predictions.

@@

\mynote{Discussion of case when individual $X_i\dotsm X_j$ are constrained}

>>>>

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2017-05-15T18:21:39+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

The probability distribution for the sample average obtained by applying
\me\ at the population level has by construction a lower entropy than the
one obtained by application at the sample level. It says that some sample
states $\yx$ should be considered less likely than in the other
distribution. The lower entropy signals the presence of an additional
physical assumption behind the former distribution. Such assumption,
intuitively, is that the sample is part of a larger population, of which it
is representative. And this assumption may affect our predictions.
\mynote{It is a very natural assumption in the neuroscientific context and
  therefore we find it preferable. In fact, also physical neuronal network
  model add an external input to the neurons, mimicking their embedding in a
  larger network}

@@

\mynote{Discussion of case when individual $X_i\dotsm X_j$ are constrained.
Likely breakdown of \me\ in this case \cite{portamana2009}. Hints at full
Bayesian treatment of which \me\ is a limit? \cite[***]{mackay1995_r2003}}
